The Small World Network Effect in Open Source Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-14 paper/main.tex
More paper progress.

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}

@@

@@

Also, measuring \textit{Path Length} ($L$) allows us to gauge how far removed developers in the graph are from one another. For example

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,8) {1};
  \node (n2) at (12,6)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (6,5)  {4};

@@

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,8) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (11,8)  {4};

@@

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,7) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (8,7)  {3};
  \node (n4) at (11,8)  {4};

  \draw ({n1}) -- ({n2});
  \draw ({n3}) -- ({n4});
  \draw ({n1}) -- ({n4});
  \draw ({n2}) -- ({n4});
\end{tikzpicture}

@@

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
\end{center}

@@

\section{Conclusion}
\section{Acknowledgments}

>>>>

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{positioning}
\setlength{\abovecaptionskip}{2pt}

@@

\textit{Graph Structure}
A bipartite graph is a specialized type of graph containing two disjoint sets of verticies. This can be denoted by $G=(P,C,E)$, where $P \cap C = \emptyset$. For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors. Each project node, therefore, is only connected to contributor nodes, and vice versa.

\begin{figure}
\label{fig:example_graphs}
\centering
\begin{tikzpicture}
\tikzset{P/.style={circle,fill=lightgray!20}}
\tikzset{C/.style={circle,fill=black!20}}

 [scale=.5,auto=left]
  \node[P] (p1) at (-5,3)  {$P_1$};
  \node[P] (p2) at (-5,2)  {$P_2$};
  \node[P] (p3) at (-5,1)  {$P_3$};
  \node[P] (p4) at (-5,0)  {$P_4$};

  \node[C] (c1) at (-2,3)  {$C_1$};
  \node[C] (c2) at (-2,2)  {$C_2$};
  \node[C] (c3) at (-2,1)  {$C_3$};
  \node[C] (c4) at (-2,0)  {$C_4$};

  \draw ({p1}) -- ({c1});
  \draw ({p1}) -- ({c2});
  \draw ({p2}) -- ({c2});
  \draw ({p2}) -- ({c4});
  \draw ({p3}) -- ({c3});
  \draw ({p4}) -- ({c3});
  \node[draw=none,fill=none,rectangle,left=1mm of p1] {Projects}; 
  \node[draw=none,fill=none,rectangle,right=1mm of c1] {Contributors}; 
\end{tikzpicture}
\caption{A caption.}
\end{figure}

This is a typical representation found in social and collaboration networks\cite{ramasco2004self}.

The collected data was organized into a graph structure $G$, with the nodes representing the projects and the edges representing one or more shared developer between projects.

@@

Also, measuring \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. For example

\begin{figure}
\label{fig:example_graphs}
\centering
\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,8) {1};
  \node (n2) at (12,6)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (6,5)  {4};
  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 0.0$};

@@

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]

  \node (n1) at (15,8) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (11,8)  {4};
  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 1.0$};

@@

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,7) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (8,7)  {3};
  \node (n4) at (11,8)  {4};
  \node[draw=none,fill=none,rectangle,right=1mm of n1] {$C^\Delta = 0.6$};

  \draw ({n1}) -- ({n2});
  \draw ({n3}) -- ({n4});
  \draw ({n1}) -- ({n4});
  \draw ({n2}) -- ({n4});
\end{tikzpicture}
\caption{A caption.}
\end{figure}

@@

Summary statistics for the graph analysis are captured in figure \ref{fig:summary_stats}. First, $S^\Delta > 1$ is observed for both the mean and the median, which meets the criteria for a small-world network\cite{humphries2008network}.\\

$Q$ and $C^\Delta$ both indicate a non-normal distribution, as shown by the large standard deviation. This observation indicates a propensity towards the extremes of these measurements. This is further reinforced by the distribution of $Q$ shown in figure \ref{fig:q_distribution}. This figure indicates that the majority of subgraphs have a $Q$ and $C^\Delta$ value of either 0 or 1.\\

Exploring this phenomenon further, follows that most graphs resemble the top or the middle graph in figure \ref{fig:example_graphs}, with relatively few resembling the bottom graph.

\begin{figure}
\label{fig:cc_popular}
\begin{center}
\caption{$C^\Delta$ of Popular Projects}
\includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{$C^\Delta$ of Unpopular Projects}
\includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
\end{center}
\end{figure}

\begin{figure}
\label{fig:q_distribution}
\begin{center}
\caption{$Q$ Distribution}
\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{$S^\Delta$ Distribution}
\includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{$C^\Delta$ and Project Popularity}
\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
\end{center}
\end{figure}

The project graph contains a large amount of subgraphs, and as a whole appears less clustered than some other observed social network graphs\cite{madey2002open}.

@@

\section{Conclusion}

\section{Acknowledgments}
